Modelling BCG vaccination in the UK

### 2019-06-19 rmds/08-model-development.Rmd
model-dev tables updated

load_formated("disease_params_table")
load_formated("demographic_params_table")
load_formated("sources_table")
#load_formated("scenarios_table")
load_formated("eff_bcg")
```

@@

```{r summary-scenarios, eval = FALSE}
kable(scenarios_table, caption = "Summary of planned scenario analyses to be carried out in the next chapter as part of model fitting by comparision of the goodness of fit to the data.", booktabs = TRUE, escape = FALSE) %>% 
  column_spec(c(1), width = "2cm") %>% 
  column_spec(c(2), width = "8cm")
```

>>>>

load_formated("disease_params_table")
load_formated("demographic_params_table")
load_formated("sources_table")
load_formated("scenarios_table")
load_formated("eff_bcg")
```

@@

```{r summary-scenarios}
kable(scenarios_table, caption = "Summary of planned scenario analyses to be carried out in the next chapter as part of model fitting by comparision of the goodness of fit to the data.", booktabs = TRUE, escape = FALSE) %>% 
  column_spec(c(1), width = "2cm") %>% 
  column_spec(c(2), width = "8cm")
```

### 2019-06-19 rmds/09-model-fitting.Rmd
model-dev tables updated

2. 2500 parameter sets were taken from the prior distribution and the model was then simulated for each one.

@@

7. SMC^2 model fitting with 3000 initial parameter particles. Particle rejuvernation was set to trigger when the effective sample size decreased below 1000, with 4 MCMC steps used each time.

@@

10. Parameter sensitivity was estimated by calculating the partial rank correlation coffecient (PRCC) for each model parameter, at each time point fitted too, for both overall TB incidence rates and TB incidence rates in children. Results were then plotted in order of the absolute magnitude of the correlation, with the direction of the correlation determined using colour. The `epiR` package was used to compute the PRCC.[@EpiR]

>>>>

2. 5000 parameter sets were taken from the prior distribution and the model was then simulated for each one.

@@

7. SMC^2 model fitting with 5000 initial parameter particles. Particle rejuvernation was set to trigger when the effective sample size decreased below 1000, with 4 MCMC steps used each time.

@@

10. Parameter sensitivity was estimated by calculating the partial rank correlation coffecient (PRCC) for each model parameter, for the final time point fitted too (2004), for both overall TB incidence rates and TB incidence rates in children. Results were then plotted in order of the absolute magnitude of the correlation, with the direction of the correlation determined using colour. The `epiR` package was used to compute the PRCC.[@EpiR]
